Bounded Model Checking for Embedded Systems \\ (Position Paper)

### 2016-01-05 paper.tex
minor changes

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The dependency on the correct functioning of embedded systems is rapidly growing, mainly due to their wide range of applications, such as micro-grids, automotive device control ({\it e.g.}, airbag control), health care, surveillance, mobile devices, and consumer electronics. Their structures are becoming more and more complex and now require multi-core processors with scalable shared memory, in order to meet increasing computational power demands. As a consequence, reliability of embedded (distributed) software becomes a key issue during system development, which must be carefully addressed and assured. Normally, state-of-the-art verification methodologies for embedded systems generate test vectors (with constraints) and use assertion-based verification and high-level processor model, during simulation; however, other additional challenges have been raised: the need for meeting time and energy constraints, handling concurrent software, dealing with platform restrictions, evaluating implementation-structure choices, and supporting legacy designs (usually written in low-level languages). The present paper discusses challenges, problems, and recent advances to ensure correctness and timeliness regarding embedded systems. Reliability issues, in the development of micro-grids and cyber-physical systems, are then considered, as a prominent model checking application.
\end{abstract}

@@

Indeed, many current embedded systems, such as unmanned aerial vehicles (UAVs) and medical monitoring systems~\cite{Cordeiro09}, become interesting solutions only if they can reliably perform their target tasks. For instance, UAVs are a trend on military missions, due to the absence of pilots; however, an incorrect plan execution may also cost human-lives, which is unacceptable. In addition, wrong disease diagnosis or condition-evaluation reports also have the potential to compromise patients' health, with serious consequences.

@@

Scratch is another example of software-model checker, which uses knowledge about the system to be verified and the underlying hardware, for detecting races related to direct memory access (DMA) in the Cell BE processor~\cite{Donaldson10}. Such a tool also uses BMC, in order to detect DMA races, and bounded model checking with \textit{k}-induction, which aims to prove the absence of races.

@@

\textbf{(RP1)} Cordeiro {\it et al.} proposed the first SMT-based BMC for full C programs, called Efficient SMT-Based Context-Bounded Model Checker (ESBMC)~\cite{Cordeiro12}, which was later extended to support C++98 programs~\cite{ECBS13}.

@@

\bibitem{Kopetz11}
H.~Kopetz.
\newblock {\em Real-Time Systems - Design Principles for Distributed Embedded Applications}.
\newblock Real-Time Systems Series, Springer, ISBN 978-1-4419-8236-0, pp. 1--376, 2011.

\bibitem{leeCPS}
E.~Lee 
\newblock {\em Cyber-physical Systems: Design Challenges.} 
\newblock In: International Symposium on Object Oriented Real-Time Distributed Computing, pp. 363--369, 2008.

@@

@@

\bibitem{Bessa16}
Bessa I., Ismail H., Cordeiro L., Chaves Filho J.:
\newblock {\em { Verification of Delta Form Realization in Fixed-Point Digital Controllers Using Bounded Model Checking.}} 
\newblock In: Design Automation for Embedded Systems (to appear), pp. 49--54, 2016.

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The dependency on the correct functioning of embedded systems is rapidly growing, mainly due to their wide range of applications, such as micro-grids, automotive device control ({\it e.g.}, airbag control), health care, surveillance, mobile devices, and consumer electronics. Their structures are becoming more and more complex and now require multi-core processors with scalable shared memory, in order to meet increasing computational power demands. As a consequence, reliability of embedded (distributed) software becomes a key issue during system development, which must be carefully addressed and assured. Normally, state-of-the-art verification methodologies for embedded systems generate test vectors (with constraints) and use assertion-based verification and high-level processor model, during simulation; however, other additional challenges have been raised: the need for meeting time and energy constraints, handling concurrent software, dealing with platform restrictions, evaluating implementation-structure choices, and supporting legacy designs (usually written in low-level languages). The present paper discusses challenges, problems, and recent advances to ensure correctness and timeliness regarding embedded systems. Reliability issues, in the development of micro-grids and cyber-physical systems, are then considered, as a prominent (bounded) model checking application.
\end{abstract}

@@

Indeed, many current embedded systems, such as unmanned aerial vehicles (UAVs) and medical monitoring systems~\cite{Cordeiro09}, become interesting solutions only if they can reliably perform their target tasks. For instance, UAVs are a trend on military missions, due to the absence of pilots; however, an incorrect plan execution may also cost human-lives, which is unacceptable. In addition, wrong disease diagnosis or condition-evaluation reports have the potential to compromise patients' health, with serious consequences.

@@

Scratch is another example of software-model checker, which uses knowledge about the system to be verified and the underlying hardware, for detecting races related to direct memory access (DMA) in the Cell BE processor~\cite{Donaldson10}. Such a tool also uses BMC, in order to detect DMA races, and BMC with \textit{k}-induction, which aims to prove the absence of races.

@@

\textbf{(RP1)} Cordeiro {\it et al.} proposed the first SMT-based BMC for full C programs, called Efficient SMT-Based Context-Bounded Model Checker (ESBMC)~\cite{Cordeiro12}, which was later extended to support C++98 programs~\cite{ECBS13} and Qt programs~\cite{Sousa15}.

@@

\bibitem{Kopetz11}
H.~Kopetz:
\newblock {\em Real-Time Systems - Design Principles for Distributed Embedded Applications}.
\newblock Real-Time Systems Series, Springer, ISBN 978-1-4419-8236-0, pp. 1--376, 2011.

\bibitem{leeCPS}
Lee E.:
\newblock {\em Cyber-physical Systems: Design Challenges.} 
\newblock In: International Symposium on Object Oriented Real-Time Distributed Computing, pp. 363--369, 2008.

@@

\bibitem{Sousa15}
Sousa F., Cordeiro L., Lima Filho E.: 
\newblock {\em { Bounded Model Checking of C++ Programs Based on the Qt Framework.}} 
\newblock In: Global Conference on Consumer Electronics, pp. 179--180, 2015.

@@

\bibitem{Bessa16}
Bessa I., Ismail H., Cordeiro L., Chaves Filho J.:
\newblock {\em { Verification of Fixed-Point Digital Controllers Using Direct and Delta Forms Realizations.}} 
\newblock In: Design Automation for Embedded Systems (to appear), pp. 49--54, 2016.
